---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
data <- read.csv("E:/Nada/Others/Courses/Data Science Specialization/Ex/Course 5/activity.csv")
processedData <- subset(data, !is.na(data$steps))
```

## What is mean total number of steps taken per day?

```{r}
sums <- aggregate(as.numeric(processedData$steps), by=list(date=processedData$date), FUN=sum)
hist(sums$x, main = "The Average Number of Steps Taken Across all Days", xlab="Interval", ylab="Average Number of Steps")
```

Mean and Median of the total number of Steps per Day
Mean:
```{r}
mean_steps <- mean(sums$x, na.rm=TRUE)
mean_steps
```

Median:
```{r}
median_steps <- median(sums$x, na.rm=TRUE)
median_steps
```

## What is the average daily activity pattern?

```{r}
avg <- aggregate(as.numeric(processedData$steps), by=list(interval=processedData$interval), FUN=mean)
plot(avg$interval, avg$x, type="l", main = "The Average Number of Steps Taken Across all Days", xlab="Interval", ylab="Average Number of Steps")
```

The maximum average is 
```{r}
max(avg$x)
```

## Imputing missing values

The number of missing values is 

```{r}
sum(which(is.na(data)))
```

Replacing the missing values by average of the time interval

```{r}
navalues <- subset(data, is.na(data))
index <- which(is.na(data))
navalues$steps[avg$interval == navalues$interval] <- avg$x
finalData <- data
finalData$steps[index] <- navalues$steps

sums <- aggregate(as.numeric(finalData$steps), by=list(date=finalData$date), FUN=sum)
hist(sums$x, main = "The Average Number of Steps Taken Across all Days", xlab="Interval", ylab="Average Number of Steps")
```

## Are there differences in activity patterns between weekdays and weekends?

```{r}
library(lubridate)
week <- weekdays(as.Date(finalData$date))
finalData$weekday <- week
```

The maximum average is 
```{r}
max(avg$x)
```